Adopting agile in the large: motivations, success factors and challenges

### 2013-11-27 journal/article.tex
Updates on coding

@@

>>>>

-- Any statement that represents its own concept is coded. The statement becomes
   a quote.

-- The statements that are quoted must related to the research questions, or
   contextual codes.

-- The concept and quote is first considered as free standing, i.e. not
   related to any existing code.

-- If there is an existing code that is close to the new code it is considered
   to use the existing code.

@@

%% -----------
